\Title

### 2020-12-10 manuscript/manuscript.tex
Minor tweaks to the text

We can improve the efficiency of the algorithm further by using only data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:stepsize} and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operations performed in steps \ref{alg:stepsize} and
\ref{alg:residual} can be done by a summation
(TODO: ADD EQUATION)
instead of a matrix-vector product, which allows us to avoid storing the larger
$N \times M_k$ Jacobian.
The influence of distance sources on the solution is maintained by using the
entire set of data points when updating the residuals vector.

>>>>

We can improve the efficiency of the algorithm further by using only data
points that fall within the $k$-th window for fitting the sources
(steps \ref{alg:scale} and \ref{alg:fit}),
while using all available data when calculating the step size and residuals
(steps \ref{alg:stepsize} and \ref{alg:residual}).
By doing so, we reduce the Jacobian matrix further to $N_k \times M_k$
elements.
The forward modeling operations performed in steps \ref{alg:stepsize} and
\ref{alg:residual} can be done by a summation
(TODO: ADD EQUATION)
instead of a matrix-vector product, which allows us to avoid computing and
storing the larger $N \times M_k$ Jacobian at any point.
The influence of distance sources on the solution is maintained by using the
entire set of data points when updating the residuals vector.
